Analysis of Data Quality Management Maturity Level at PT Bank XYZ\\

### 2024-12-26 paper.tex
Changes from papeeria

\section{Introduction}
Organizations today generate and manage data from a variety of sources, requiring robust systems to handle customer profiles, financial transactions, account management, and credit applications. Managing data quality (DQM) has become a critical focus for organizations, particularly in the banking sector, where accurate and reliable data serves as a cornerstone for operational efficiency and strategic growth. Poor data quality can lead to inaccuracies that hinder decision-making, such as selecting optimal business locations, and can expose organizations to reputational and financial risks.

In the context of PT Bank XYZ, understanding the maturity level of Data Quality Management (DQM) is crucial to identify gaps and opportunities for improvement. The bank operates in a complex data ecosystem, integrating Core Banking Systems (CBS), Customer Relationship Management (CRM) platforms, and regulatory compliance tools. These systems demand high data quality to meet operational needs and comply with regulations, such as POJK No. 8/2023 on Anti-Money Laundering and Counter Terrorism Financing.

To address these challenges, this paper explores the data quality maturity level of data quality management at PT XYZ and outlines strategies to enhance its governance framework. The study emphasizes the need for a holistic approach to data integration, quality monitoring, and regulatory compliance to ensure sustainable growth and resilience in the face of increasing data demands.

The study is guided by the following research questions:
\begin{enumerate}
    \item What is the current maturity level of data quality management at PT XYZ?
    \item How can PT XYZ improve its data quality management practices to address regulatory, operational, and strategic risks?
\end{enumerate}

>>>>

\section{Introduction}
% Organizations today generate and manage data from a variety of sources, requiring robust systems to handle customer profiles, financial transactions, account management, and credit applications. Managing data quality (DQM) has become a critical focus for organizations, particularly in the banking sector, where accurate and reliable data serves as a cornerstone for operational efficiency and strategic growth. Poor data quality can lead to inaccuracies that hinder decision-making, such as selecting optimal business locations, and can expose organizations to reputational and financial risks.

% In the context of PT Bank XYZ, understanding the maturity level of Data Quality Management (DQM) is crucial to identify gaps and opportunities for improvement. The bank operates in a complex data ecosystem, integrating Core Banking Systems (CBS), Customer Relationship Management (CRM) platforms, and regulatory compliance tools. These systems demand high data quality to meet operational needs and comply with regulations, such as POJK No. 8/2023 on Anti-Money Laundering and Counter Terrorism Financing.

% To address these challenges, this paper explores the data quality maturity level of data quality management at PT XYZ and outlines strategies to enhance its governance framework. The study emphasizes the need for a holistic approach to data integration, quality monitoring, and regulatory compliance to ensure sustainable growth and resilience in the face of increasing data demands.

% The study is guided by the following research questions:
% \begin{enumerate}
%     \item What is the current maturity level of data quality management at PT XYZ?
%     \item How can PT XYZ improve its data quality management practices to address regulatory, operational, and strategic risks?
% \end{enumerate}

Organizations today generate and manage data from a variety of sources, requiring robust systems to handle customer profiles, financial transactions, account management, and credit applications. Managing data quality (DQM) has become a critical focus for organizations, particularly in the banking sector, where accurate and reliable data serves as a cornerstone for operational efficiency and strategic growth. Poor data quality can lead to inaccuracies that hinder decision-making, such as selecting optimal business locations, and can expose organizations to reputational and financial risks.

PT Bank XYZ, a microfinance-focused bank headquartered in Kabupaten Bandung Barat, operates a network of 24 branches and one cash office across Java, serving diverse customer needs through products like savings, deposits, and credit. As of October 2024, the bank manages assets of Rp 366 billion and employs approximately 300 staff, including an Information Technology (IT) division responsible for supporting business data analysis, regulatory reporting, and information systems. Despite its growth, the bank faces significant challenges, including fragmented data sources, increasing demands for internal and external data reporting, and frequent penalties from regulators such as OJK due to reporting errors. Additionally, regulatory requirements like POJK No. 8/2023 on Anti-Money Laundering and Counter-Terrorism Financing underscore the importance of accurate and up-to-date data management practices.

In the context of these challenges, understanding the maturity level of DQM at PT Bank XYZ is critical to identifying gaps and uncovering opportunities for improvement. The bank operates in a complex data ecosystem that integrates Core Banking Systems (CBS), Customer Relationship Management (CRM) platforms, and Loan Origination Systems (LOS), among others, without mechanisms for aggregating or monitoring data quality. As the organization strives to improve digital services and ensure compliance with evolving regulatory standards, addressing the risks of poor data quality—such as reputational damage, reporting errors, financial losses, and strategic missteps—becomes essential.

To address these challenges, this paper explores the maturity level of data quality management at PT Bank XYZ and outlines strategies to enhance its governance framework. The study emphasizes the need for a holistic approach to data integration, quality monitoring, and regulatory compliance to ensure sustainable growth and resilience in the face of increasing data demands. This study is structured around two primary research questions: First, it seeks to determine the current maturity level of data quality management (DQM) at PT Bank XYZ. Second, it aims to explore strategies for improving the bank’s DQM practices to address regulatory, operational, and strategic risks effectively.
